Towards realtime detection of compact binary coalescence to improve the prospects for multimessenger astronomy\editorial{Submit to PRD or CQG?}

### 2011-03-01 results.tex
results: double checked max duration, so un-highlighted it
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@669 ccdd05d5-56c1-461a-bf98-85f6876523b4
results: took out editorial about --taper-injections
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@670 ccdd05d5-56c1-461a-bf98-85f6876523b4

For each run, we performed about $10^4$ injections into our mock dataset.  Injections were 2PN post-Newtonian inspiral waveforms with component masses independently and identically distributed in $[1, 3]$ $M_\odot$.  Injections were tapered \editorial{Check --taper-injection option with Drew.} at a frequency of 10~Hz where they enter the Advanced \textsc{ligo} detection band.  This dictated that the longest injection waveform had a duration of {\color{red} 1~777~s}.  In order to guarantee that no two injection waveforms overlapped in the data, the coalescence times of injections were spaced apart by {\color{red} 2~000~$\pm$~100~s}.  For the sake of economizing disk space, we simultaneously analyzed {\color{red} 16 statistically independent sets} of about $10^3$ injections apiece in the same {\color{red} 14 day} stretch of mock strain data.

>>>>

For each run, we performed about $10^4$ injections into our mock dataset.  Injections were 2PN post-Newtonian inspiral waveforms with component masses independently and identically distributed in $[1, 3]$ $M_\odot$.  Injections were tapered at a frequency of 10~Hz where they enter the Advanced \textsc{ligo} detection band.  This dictated that the longest injection waveform had a duration of 1~777~s.  In order to guarantee that no two injection waveforms overlapped in the data, the coalescence times of injections were spaced apart by {\color{red} 2~000~$\pm$~100~s}.  For the sake of economizing disk space, we simultaneously analyzed {\color{red} 16 statistically independent sets} of about $10^3$ injections apiece in the same {\color{red} 14 day} stretch of mock strain data.
